Robots, Are They Overlords or Serf-Laborers?

### 2015-06-13 draft1.tex
Edit 'The Most Profound Issues of Robotics' section

\section{The Most Profound Issues of Robotics}
From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society.
This section synthesizes the issues risen by the creation of AI and employment robots in a wide spectrum of tasks.

>>>>

\section{The Most Profound Issues of Robotics}
From the very early contemplations of AI, it has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
Near future is fecund to many dilemmas which humankind, soon or later, will face regarding AI's moral integrity and its position in society.
This section synthesizes the issues of employment of AI and robots in a wide spectrum of tasks.
